---
title: "R Notebook"
output: html_notebook
---
1. Write a R code to Generate 6X6 matrix

```{r}
#(A) using the random numbers between 1 to 100 &amp; generate another 6x6 matrix
a <- sample(1:100)
b <- sample(500:600)
A <- matrix(a, nrow = 6, ncol = 6)
B <- matrix(b, nrow = 6, ncol = 6)
A
B
```
a. Find the range of matrices A and B.
```{r}
range(A)
range(B)
```

b. Find the max value from each row of the matrices A and B.
```{r}
apply(A,1,max)
apply(B,1,max)
```

c. Find the diagonal values of matrices A&amp;B.
```{r}
z <- A / B
diag(t(z))
```

d. Multiply matrices A and B
```{r}
A %*% B
```

e. Replace the 4th row of Matrix A with diagonal values of matrix B
```{r}
A[4, ] <- diag(t(B))
```

f. Multiply matrices A &amp; B and store the values on X.
```{r}
X <- A %*% B
```

g. Divide the matrix A with matrix B.
```{r}
A / B
```

2. Create a table using dataframe/tibble with the following categories(a to f)

a. First name,
b. Second Name,
c. Age,
d. Occupation,
e. Place,
f. Random numbers( between 1 to 10)
```{r}
fn<-c("Pheak","Kimmonyvorn","Dalya","Menghong","Bongrong","Dara","Panha","Jenny","Lynan","Leapheng")
ln<-c("Am","Chea","Chea","Chean","Daro","Chor","Kit","Sun","Thon","Ty")
ag<-c(19,19,22,21,20,19,18,19,21,19)
occ<-c("Student","Student","Student","Student","Student","Student","Student","Student","Student","Student")
pl<-c("kpc","bcm","pp","pp","sr","pp","kd","btb","bmc","btb")
rn<-sample(1:10,10,replace = TRUE)
tabledata<-data.frame(FirstName=fn,LastName=ln,Age=ag,Occupation=occ,Place=pl,RandomNumber=rn)
tabledata

```
g. Extract the last column (f)
```{r}
last_column<-tabledata$RandomNumber
last_column
```

h. Find the sum, mean and length of the extracted colum
```{r}
sum(last_column)
mean(last_column)
length(last_column)
```

3.Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from
the official news agency’s website(link: https://www.khmertimeskh.com/50801787/covid-19-cambodia-relaxes-restrictions-singapore-indonesia-promotes-vaccination-plans/ )

#a. Read the .txt file
```{r}
library(tokenizers)
text <- read.delim("new.txt")

```
#b. Perform the Tokenization &amp; count the words
```{r}
words_text <- paste0(text)
tokens <- tokenize_words(words_text)
count <- count_words(words_text)
count
```
#c. Identify the most repeated word and replace that word with “KIT”
```{r}
repleated_words <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
repeated_words_count <- max(table(tokens))
subs <- gsub("the", "KIT", tokens)
repleated_words
repeated_words_count
subs
```
d. Perform the Sentiment analysis
```{r}
library("syuzhet")
library("ggplot2")
sentiment_analysis <- get_sentiment(tokens, method="syuzhet")
summary(sentiment_analysis)

```

e. Plot the graph between “words count” and “words” using geom_col()
e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color,
Center, space between graph and title = 20.
```{r}
 
```

4. Find the assigned Dataset from the list below and perform the following
#a. Import and Clean the dataset.
```{r}
dataset <- read.csv("draymond.csv")
dataset
#the dataset is already clean there is no NA.
```

b. Find the x and y variables(axis) from the assigned dataset and give the reason for
selecting the x and y axis.
```{r}
## selecting Player Name as X and Year as Y
plot <- ggplot(dataset, aes(x=player, y=season)) + 
    xlab("Player Name") +
    ylab("Year")
```

c. Plot the graph using geom_col() and perform the linear model in statistics.
```{r}
# using geom_col
plot <- plot+geom_col()

#perform linear model in smooting
plot <- plot+geom_smooth(method="lm")
```

d. Perform the facet with the available columns(Choose the any two variables from the
columns)
```{r}
# use facet with 2 variable by possessions and year
plot+facet_grid(possessions~season)
# use facet with 1 variable by the year
plot <- plot+facet_wrap(~season)
plot
```


e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis &amp;
graph)
e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space
between graph and title = 20.
e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space
between graph and title = 20.
e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space
between graph and title = 25.

```{r}
plot <- plot +
  ggtitle("Possessions") + theme(
  axis.title.x=element_text(size=10, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
  axis.title.y=element_text(size=10, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
  plot.title=element_text(size=25, color="blue", face="bold", margin=margin(t=25,r=0,b=25,l=0))
  )
plot

```

